--- 
title: "Football Players' Value and Wage"
author: "Yuehan Hu & Wenchen"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

# Introduction
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Introduction:
There are a lot of datasets on kaggle, I chose the Football (FIFA - 2019) Dataset.
This Dataset Contains all Information of players who participated in the FIFA-2019 League.
This Dataset consists of 89 Features including the parameters, by which a Player's ability can be measured some of the parameters included in the dataset are,
Age, Skill Moves, Work Rate, Body Type, joined year, Agility.
This data set is large and can be used for data cleaning, data transformation, missing value processing, and data visualization, to explore the factors that affect Football Players' Value and Wage, and to explore the factors affecting Football Players' Value and Wage in a multi-dimensional way. factors to explore which factors have a significant impact on Football Players' Value and Wage.

<!--chapter:end:index.Rmd-->

---
title: "Proposal"
author: 'Yuehan Hu & Wen Chen'
date: '2022-10-29'
output: html_document
---
```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Proposal:
Analysis of Factors Affecting Football Players' Value and Wage
It is well known that players' Value and Wage are affected by multiple factors, and there are many differences in Wage of different players. We will explore the factors that affect players' Value and Wage through data visualization.
This Dataset Contains all Information of players who participated in the FIFA-2019 League.
This Dataset consists of all the parameters, which a Player's ability can be measured
some of the parameters included in the dataset .This article will explore the factors that affect player Value and Wage through data visualization methods.
Data sources:
Football (FIFA - 2019) Dataset
Football (FIFA-2019) World Cup Dataset of Players' Statistics with Notebook
This Dataset consists of 89 variables.
Age: Age of Player
Skill Moves: Describes various skill set of the player
Work Rate: Work rate of player
Body Type: Body type of player (like High, lean, Courtois, moderate)
joined year: Joining year of player
Agility: Agility of player (numerical values)
SprintSpeed: Sprinting Speed of player
Reactions: Reaction on the Numerical Scale
Potential: player's potential
Overall: All-round ability of players
URL: (https://www.kaggle.com/datasets/devansodariya/football-fifa-2019-dataset?resource=download)







<!--chapter:end:proposal.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data 

## Sources

## Cleaning / transformation

## Missing value analysis


<!--chapter:end:data.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Results

<!--chapter:end:results.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Interactive component



<!--chapter:end:interactive.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Conclusion


<!--chapter:end:conclusion.Rmd-->

